Structural controllability of ecological networks

### 2018-06-28 paper/supp-info.Rmd
Typo in table label
Adapt figure in supp materials for having 3 deltas
#50

```{r fig-rho-sensitivity, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="A sensitivity analysis of the impact of interspecific competition parameter $\\rho$ on structural stability reveals that the choice of parameters has a negligible impact on the results. (a) Spearman correlation coefficient of the contribution to stable coexistence of species. Lighter lines indicate the correlation coeficient for each of the twenty empirical networks. The dark line indicates the median value. (b) Difference between the conribution to stable coexistence of critical and redundant species for different values of the iterspecific competition parameters $\\rho$.", fig.pos="p", fig.align='center'}
drake::loadd(fig_rho_sensitivity)
fig_rho_sensitivity %<>% add_internal_margins()
cowplot::plot_grid(plotlist = fig_rho_sensitivity, ncol = 2, align = "h")
```

@@

```{r tab-asumption-visitation}
drake::loadd(visitation_importance_agreement)

>>>>

```{r fig-rho-sensitivity, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]], fig.cap="A sensitivity analysis of the impact of interspecific competition parameter $\\rho$ on structural stability reveals that the choice of parameters has a negligible impact on the results. (a) Spearman correlation coefficient of the contribution to stable coexistence of species. Lighter lines indicate the correlation coeficient for each of the twenty empirical networks. The dark line indicates the median value. (b) Difference between the conribution to stable coexistence of critical and redundant species for different values of the iterspecific competition parameters $\\rho$.", fig.pos="p", fig.align='center'}
drake::loadd(fig_rho_sensitivity)
fig_rho_sensitivity %<>% add_internal_margins()
cowplot::plot_grid(plotlist = fig_rho_sensitivity, ncol = 1, align = "hv")
```

@@

```{r tab-assumption-visitation}
drake::loadd(visitation_importance_agreement)
